\documentclass[a4paper,20pt]{article}

\usepackage{latexsym}
\usepackage[empty]{fullpage}
\usepackage{titlesec}
\usepackage{marvosym}
\usepackage[usenames,dvipsnames]{color}
\usepackage{verbatim}
\usepackage{enumitem}
\usepackage[pdftex]{hyperref}
\usepackage{fancyhdr}

\pagestyle{fancy}
\fancyhf{} % clear all header and footer fields
\fancyfoot{}
\renewcommand{\headrulewidth}{0pt}
\renewcommand{\footrulewidth}{0pt}

% Adjust margins
\addtolength{\oddsidemargin}{-0.530in}
\addtolength{\evensidemargin}{-0.375in}
\addtolength{\textwidth}{1in}
\addtolength{\topmargin}{-.45in}
\addtolength{\textheight}{1in}

\urlstyle{rm}

\raggedbottom
\raggedright
\setlength{\tabcolsep}{0in}

% Sections formatting
\titleformat{\section}{
  \vspace{-10pt}\scshape\raggedright\large
}{}{0em}{}[\color{black}\titlerule \vspace{-6pt}]

%-------------------------
% Custom commands
\newcommand{\resumeItem}[2]{
  \item\small{
    \textbf{#1}{#2 \vspace{-2pt}}
  }
}

\newcommand{\resumeItemNew}[2]{
  \item{
    \textbf{#1}{#2 \vspace{-2pt}}
  }
}

\newcommand{\resumeItemWithoutTitle}[1]{
  \item\small{
    {\vspace{-2pt}}
  }
}

\newcommand{\resumeSubheading}[4]{
  \vspace{-1pt}\item
    \begin{tabular*}{0.97\textwidth}{l@{\extracolsep{\fill}}r}
      \textbf{#1} & \textit{#2} \\
      \textit{#3} & \textit{#4} \\
    \end{tabular*}\vspace{-5pt}
}


\newcommand{\resumeSubItem}[2]{\resumeItem{#1}{#2}\vspace{-3pt}}

\newcommand{\resumeSubItemNew}[2]{\resumeItemNew{#1}{#2}\vspace{-3pt}}

\renewcommand{\labelitemii}{$\circ$}

\newcommand{\resumeSubHeadingListStart}{\begin{itemize}[leftmargin=*]}
\newcommand{\resumeSubHeadingListEnd}{\end{itemize}}
\newcommand{\resumeItemListStart}{\begin{itemize}}
\newcommand{\resumeItemListEnd}{\end{itemize}\vspace{-5pt}}

%-----------------------------
%%%%%%  CV STARTS HERE  %%%%%%

\begin{document}

%----------HEADING-----------------
\begin{tabular*}{\textwidth}{l@{\extracolsep{\fill}}r}
  \textbf{{\LARGE Vinay Dinkar Kale}} & Email: \href{mailto:vinaykale64@gmail.com}{vinaykale64@gmail.com}\\
  \href{https://vinaykale64.github.io}{Portfolio: vinaykale64.github.io} & Mobile:~~~+1-646-510-1024 \\
  \href{https://github.com/vinaykale64}{Github: ~~github.com/vinaykale64} \\
\end{tabular*}

%-----------EDUCATION-----------------
\vspace{0pt}
\section{Education}
  \resumeSubHeadingListStart
    \resumeSubheading
      {Columbia University, New York}{NYC, New York}
      {M.S. Data Science}{2017 - 2018}
      {\scriptsize { \small{\newline{}{Relevant Coursework:} Probability Theory, Statistics, Machine Learning, NLP, Deep Learning, Algorithms, Data Storytelling }}}
    \resumeSubHeadingListEnd
    \vspace{-10pt}
  \resumeSubHeadingListStart
    \resumeSubheading
      {Indian Institute of Technology Madras (IIT Madras)}{Chennai, India}
      {B.Tech Mechanical Engineering, M.Tech Product Design}{2011 - 2016}
      {\scriptsize { \small{\newline{}{Relevant Coursework:} Computational Engineering, Time Series Analysis, Regression Models, Operations Managment}}}
    \resumeSubHeadingListEnd
    
%-----------SKILLS-----------------

\vspace{-5pt}
\section{Skills}
	\resumeSubHeadingListStart
	\resumeSubItemNew{Languages}{~~~~~~Python, R, SQL, Spark, Scala, Julia, C, C++, LaTeX}
	\resumeSubItemNew{Frameworks}{~~~~Scikit, Dask, Plotly, Dash, TensorFlow, Keras, PyTorch, RShiny, Django, Flask, Tableau, MS Office}
	\resumeSubItemNew{Platforms}{~~~~~~~Docker, GIT, Airflow, MySQL, Linux, AWS, GCP, Microsoft Azure, Heroku, Jenkins, Travis}

%-----------Experience-----------------

\resumeSubHeadingListEnd
\vspace{-5pt}
\section{Experience}
  \vspace{2pt}
  \resumeSubHeadingListStart
    \resumeSubheading{Capital One, New York}{}
    {Senior Data Scientist}{2019 - Present}
    \resumeItemListStart
        \resumeItemNew{}
          {Worked on building cloud-based end-to-end credit card underwriting ML model deployed via a dockerized Python API, affecting more than 100M Customers, with estimated incremental value of \$35M per year}
          \resumeItemNew{}{Led development of agile model monitoring and validation framework with domain experts, decreasing the time and effort required to complete compliance-required monitoring from a week to 8 hours.}
          \resumeItemNew{}
          {Advised on refactor of python libraries from partner teams with focus reusability, architecture and design.}
          \resumeItemNew{}{Coached junior data scientists on developer habits like code quality, testing, documentation and git workflows}
      \resumeItemListEnd
      
\vspace{5pt}
    \resumeSubheading
		{Spotify, New York}{}
		{Data Scientist}{Summer 2018}
		\resumeItemListStart
        \resumeItemNew{}
          {Worked closely with cross-functional teams of analysts, user researchers, product owners and engineers to develop a fan-artist pair segmentation pipeline which quantified the affinity for 20 billion fan-artist pairs}
        \resumeItemNew{}
          {With that, analyzed how a new video overlay feature affects a typical fan-artist journey and how different fan segments engage with it, by statistical analysis on data from AB tests}
        \resumeItemNew{}
          {Other Projects: Optimised data pipelines through Google Bigquery, Redesigned artist tiering dashboard}
          
           
		\resumeItemListEnd

\vspace{5pt}
    \resumeSubheading
		{ZS Associates, India}{}
		{Data Scientist}{2016 - 2017}
		\resumeItemListStart
        \resumeItemNew{}
          {Built a intelligent Medical API for Pharmaceutical clients using patient-data vector embeddings (similar to Word2Vec) trained on sequential big medical data. This served as input to patient-level classification models.}
        \resumeItemNew{}
          {Led project in a client-facing role for marketing-mix based spend analyzer pipeline which calculates impacts of different marketing campaigns. Helped secure continued engagement for similar projects down the line.}
        \resumeItemNew{}
          {Spearheaded effort within the company for reproducibility by on-boarding all projects with git version control and setting precedent for consistent user and developer documentation.}
		\resumeItemListEnd

\resumeSubHeadingListEnd

%-----------Publications-----------------

\vspace{-10pt}
\section{Research}
\resumeSubheading
		{\href{https://openaccess.thecvf.com/content_cvpr_2018_workshops/w3/html/Mao_AIC2018_Report_Traffic_CVPR_2018_paper.html}{CVPR Conference 2018: Traffic Surveillance Research Paper}\\}{ }
		{}{ }
		\resumeItemListStart
        \resumeItemNew
          {}
          {Novel Mask-RCNN method for object detection and localization, vehicle tracking and vehicle re-identification.}
		\resumeItemListEnd

%-----------PROJECTS-----------------
\vspace{0pt}
\section{Projects}
    \resumeSubheading
		{\href{https://pypi.org/project/euphony/}{Euphony}: Python Package on PyPI\\}{ }
		{}{ }
		\resumeItemListStart
        \resumeItemNew
          {}
          {Get alerts while running time-consuming code. With a simple wrapper, it plays classical music while the code completes. It also lets user choose among artists. Future development includes ability t play external mp3 files.}
		\resumeItemListEnd
		
    \resumeSubheading
		{\href{https://stock-app-vk94.herokuapp.com}{Market-Monitor}: Live web-app to monitor financial markets\\}{}
		{}{}
		\resumeItemListStart
        \resumeItemNew{}
          {Study stock and options prices with latest news for any company. The app uses Yahoo Finance APIs for data, Dash for visualization and  Heroku for app deployment. It comes with a developer guide for documentation.}
		\resumeItemListEnd

%-----------Teaching and Volunteer Experience-----------------

\vspace{0pt}
\section{Volunteer Experience}
	\resumeSubheading
    {Organizing Committee, PyData Conference NYC}{Summer 2019}
    {Led team for reviewing proposals and spearheaded the Diversity Scholarship Initiative}{}
    \newline
    \resumeSubheading
    {Teaching Assistant, Columbia University}{2018}
    {Applied Machine Learning, Applied Deep Learning.}{}

\resumeSubHeadingListEnd

\end{document}